IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/abstract.tex
Fix up abstract
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security, untrusted JavaScript libraries and
    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
    of information flow control.
We present a coarse-grained IFC system that
can be implemented  non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central concept is an isolation mechanism whose operation does not
depend too much on the details of the programming language used.
We thus present a \emph{general} method for adding IFC to existing
languages that is largely \emph{indifferent} to the choice of language.
Additionally, we describe how to relate optimized concrete implementations
to the IFC systems produced by our technique and show how various
proposed and existing IFC systems conform to our formal framework
and therefore enjoy the semantic properties we prove.
\end{abstract}

>>>>

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security, untrusted JavaScript libraries and
    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
    of information flow control.
We formally specify a coarse-grained dynamic IFC system that
can be implemented non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central idea is that an IFC system should model
a set of communicating isolated language runtimes.
The result is a general method for adding IFC to existing
languages that is largely indifferent to the choice of language.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}
